Investigating shape standardization using geometric morphometry of pottery from Iron Age northeastern Taiwan

### 2020-04-23 analysis/paper/paper.Rmd
revise the caption for pot image

```{r, KWL-pots, fig.cap = "The Kiwulan pot (left) and an example of pottery drawing used in this paper (right)", fig.width=image_width_2_col_inch}
knitr::include_graphics(here("analysis", "figures", "pots.png"))
```

@@

We used scans of pottery drawings (Figure \@ref(fig:KWL-pots)) acquired from the Bureau of Cultural Affairs in Yilan. All drawings present a two-dimensional view of vessel cross-sections with indications of metric measurements. The scanned drawings were imported into Inkscape (http://inkscape.org) where outlines were traced manually. Where only half cross-section images were available, these were duplicated, flipped, and then joined with another one to create a 2D closed outline for each vessel. Geometric morphometric analyses were conducted using the R software (R Core Team, 2019) and the functions included in the Momocs, a R package intended to quantify and analyze shapes ([@Bonhomme2014]. The digilized outlines were converted into a list of successive xy pixel coordinates for elliptic Fourier analysis (EFA). The harmonic coefficients generated by EFA were analyzed by principal component analysis (PCA) for dimensionality reduction to illustrate the diversity of the shape data and identify major patterns of variation.

>>>>

```{r, KWL-pots, fig.cap = "A typical pot from Kiwulan (left) and an example of a pottery drawing used for outline analysis (right)", fig.width=image_width_2_col_inch}
knitr::include_graphics(here("analysis", "figures", "pots.png"))
```

@@

We used scans of pottery drawings (Figure \@ref(fig:KWL-pots)) acquired from the Bureau of Cultural Affairs in Yilan. All drawings present a two-dimensional view of vessel cross-sections with indications of metric measurements. The scanned drawings were imported into Inkscape (http://inkscape.org) where outlines were traced manually. Where only half cross-section images were available, these were duplicated, flipped, and then joined with another one to create a 2D closed outline for each vessel. Geometric morphometric analyses were conducted using the R software (R Core Team, 2019) and the functions included in the Momocs, a R package intended to quantify and analyze shapes [@Bonhomme2014]. The digilized outlines were converted into a list of successive xy pixel coordinates for elliptic Fourier analysis (EFA). The harmonic coefficients generated by EFA were analyzed by principal component analysis (PCA) for dimensionality reduction to illustrate the diversity of the shape data and identify major patterns of variation.
